%introduction
\documentclass[../../main/main.tex]{subfiles}

\pagenumbering{arabic}

\begin{document}
\glsresetall

\chapter{Introduction}
 Imagine this scene from the movie titled "The Kingdom" \cite{kingdom}.  It is a bright, sunny day in Saudi Arabia.  The compound is isolated from the rest of the Kingdom and heavily guarded by Saudi police.  The American civilian contractors are free to enjoy the American culture they are accustomed to without offending the locals.  A large group of contractors and their families are enjoying their day off watching a game of little league on the compound.  
 
 
Unexpectedly, two men dressed in Saudi police uniforms begin showering the crowd with machine gun fire.   Civilian men, women, and children run screaming for cover. The two gun men are eventually neutralized by Saudi police officers.  Saudi police yell to the survivors "come this way" to lure them away from the carnage. One of these men dressed in a police uniform shouts "Allah Akbar" and detonates, killing himself and several others near him. 

What went wrong?  How did these terrorists gain access to a secured compound?  

Movies like this and the news are bringing the reality of security to the forefront of everyone's mind.   Everyone is concerned with controlling access to their information, their property, and more importantly their lives.   

To drive it home, consider the importance of access control in computer driven cars, bank accounts, medical records, pace makers, etc.  Access control can be as simple as providing your daughter with a secret password for who can pick her up from school or as complicated as managing access to national security secrets.  In any and every system that requires some form of security, access-control is one of the foremost considerations. The work discussed in this master thesis focuses on the critical property of access control in systems security engineering.

This chapter provides an introduction to this master thesis.  It briefly touches upon the field of systems security engineering and the subspecialty of access-control by way of complete mediation.  It then introduces an approach to verifying and documenting this property using the Certified Security by Design (\glsentryshort{csbd}) approach.  After introducing the \glsentryshort{csbd}, this chapter presents an application of \glsentryshort{csbd} that aims to close the gap in its field of applicability.  It discuss how \glsentryshort{csbd} is applied to a non-automated, human-centered military system (patrol base operations).  Finally, this chapter offers the reader a glimpse at what to expect in the subsequent chapters.

      %%%%%%%%%%%%%%%%%%%% Section csbd %%%%%%%%%%%%%%%%%%%%%%
\section{In Context of Systems Security Engineering}\label{sec:intro:motivation}
The authority on standards in systems engineering is the International Organization for Standardization (ISO).  In one of its published standards (ISO/IEC/IEEE 15288 \cite{iso15288}) it describes systems engineering guidelines for managing man-made systems.  These man-made systems span the range from human-centered systems to fully automated systems.  An example of a human-centered system is a partially- or non-automated system for controlling access to a base or compound.  An example of a fully automated system is the computer that controls a driverless car.  In all these systems, security is often a critical component of the systems engineering process.


The recognized authority in systems security engineering, a subspecialty of systems engineering, is the National Institute for Standards and Technology (NIST) Special Publication 800-160 (vol 1 and vol 2) \cite{NIST800160}.  It describes a framework for designing trustworthy systems by engineering security into the system from the start.  

A subspecialty of systems security engineering manages access to security-sensitive objects using the principle of complete mediation.  Complete mediation broadly refers to verifying and documenting authentication and authorization of access to security sensitive objects. 


\section{Certified Security by Design (CSBD)}\label{sec:intro:motivation}
CSBD is an approach to verifying and documenting that a system's design satisfies the property of complete mediation. It uses formal methods by way of an access-control logic (\glsentryshort{acl}) that is implemented in an interactive theorem prover.  Formal methods add a mathematical rigor to the verification process.  The \glsentryshort{acl} is a formal propositional logic.  The interactive theorem prover takes the rigor a step further by using computer-aided reasoning in a trusted implementation.   The result is a set of formal proofs that both verify and document that the system's design is trustworthy with respect to complete mediation.  This set of formal proofs is verifiable and reproducible by independent third parties. 

It is a straight forward process to apply CSBD.  First, security-sensitive objects are identified.  For example, a secured compound or bank account information are security-sensitive objects.  Then properties of access control are described in terms of authentication and authorization.  For example, authentication may reIy on ID badges or atm cards.   Authorization may be described in a policy that determines who is authorized to access the compound or who is authorized to access bank account funds.  Additionally, modification and access rights may also be described in terms of ordered security and integrity labels.  For example, security labels for a bank account may include r (read only) $\leq$ d (deposit) $\leq$  w (withdraw).  Account owners may be granted the highest integrity level of withdraw, whereas bank managers may only be granted read  access.   The owner can read, deposit, and withdraw funds from the account.  The bank manager can only read funds from the account.  Integrity labels may include st (standard service) $\leq$ gl (gold service) $\leq$ pr (premium service).  If standard services include checking account fees and gold services do not and the account owner has a gold services account, then the owner should not be subject to the standard services checking account fees.  Furthermore, standard services account holders should not be granted gold service privileges because it would lessen the value of those service.

 Next, the system is described in \glsentryshort{hol} wherein properties of complete mediation are verified.  This verification is a set of formal proofs that are included with the system's documentation.  Full disclosure of methods are included so that the proofs can be verified and reproduced by independent third parties.




\section{Extending The Range of Applicability}\label{sec:intro:motivation}
CSBD is a core requirement for the Master of Science degree in Cybersecurity at Syracuse University.  It is also part of the Air Force Research Laboratory's STPA-Sec doctrine.   But, up until now, CSBD has been applied to automated systems.  For example, CSBD has been used with JPMC's SWIFT protocols \cite{pkm} and the F-18 Viper UAV payload controller and secure memory loader verifier (SMLV).  But, systems engineering spans the range of fully automated to non-automated, human-centered systems.  This master thesis aims to close the gap of \glsentryshort{csbd} applicability by applying it to a non-automated, human-centered system.  The aim is to determine if it can be done and if so to demonstrate it.

To accomplish this goal, patrol base operations are chosen as an example of a non-automated, human centered system.  Patrol base operations are described in the U.S. Army Ranger Handbook \cite{rangermanual}.  A security matter expert from the U.S. Army is employed to interpret the patrol base operations.  

The patrol base operations are first discussed with regards to security, assets, and unacceptable asset losses.  From there, the patrol base operations are described as a hierarchy of secure state machines.  The top level represents the most abstract description of the patrol base operations.  The descriptions become less abstract as the hierarchy descends.  Once the hierarchy is designed, it is implemented in \glsentryshort{hol}.  Properties of complete mediation are proved and documented.  
 
Application of \glsentryshort{csbd} to these patrol base operations is a success.   The hierarchical approach is an easy way to describe large systems in a manageable way. Secure state machines ease the process of proving complete mediation because it is built into the structure of the secure state machines.  In addition, a variety of insights are obtained including multiple representations of the operations, possible application to partially automated accountability systems, and a greater understanding of the operations themselves. 

 Most of the work comes in the creativity of designing the system in a manner that affords itself to verification of complete mediation.  Thus, there were no limitations found in this work as to the applicability of the \glsentryshort{csbd}. 


In summary, this work finds that \glsentryshort{csbd} is effective on non-automated, human-centered systems by way of example on patrol base operations.  This closes the gap in \glsentryshort{csbd} applicability by including these types of systems at one end of the range from fully automated to fully non-automated systems.  It's importance is derived from the importance of access-control in systems security engineering.  It is simply a method that works and does so effectively.  

\section{This Master Thesis}\label{sec:thismasterthesis}
Subsequent chapters in this master thesis describe relevant background and details of \glsentryshort{csbd} applied to patrol base operations.  The chapters begin with abstract descriptions of the patrol base operations in the context of the specific chapter.  Each chapter adds sufficient detail that subsequent chapters should be more easily understood if read in order.  Nonetheless, there are sufficient references to previous chapters if the reader wishes to skip around.


Chapter \ref{chp:background} discusses background material that may be helpful to the reader in understanding the following chapters.  Chapter \ref{chp:sse} discusses the hierarchical model of the patrol base operations in the context of systems engineering and systems security engineering.  Chapter \ref{chp:csbdacl} describes Certified Security by Design and the access-control logic in detail.  It also discusses the \glsentryshort{hol} implementation of the \glsentryshort{acl}.  Chapter \ref{chp:pb} describes the hierarchical model of the patrol base operations. Chapter \ref{chp:ssmmodel} describes secure state machines and their \glsentryshort{hol} implementation.  Chapter \ref{chp:pbssm} describes the implementation of several patrol base operations secure state machines in \glsentryshort{hol}.  Chapter \ref{chp:other} describes additional models that are discussed throughout the project, but not implemented in \glsentryshort{hol}.  Chpater \ref{chp:discussion} provides some discussion of the findings that are not covered in previous chapters.  Finally, Chapter \ref{chp:future} discusses future work and implications. 

The appendices include pretty-printed \glsentryshort{hol}-generated output of all the \glsentryshort{acl} theorems.  They also contain the code for all the \glsentryshort{hol} theorems both as pretty-printed \glsentryshort{hol}-generated output and the actual code.  There is also an appendix describing the folder structure of the files included with this thesis.


As the example at the start of this chapter makes clear, access control is a serious matter.  Systems should be designed with security from the start.   Certified Security by Design (\glsentryshort{csbd})  is an effective approach to designing trustworthy systems with respect to access control.  It does this using formal methods and computer-aided reasoning to verify and document the property of complete mediation.

The next chapter provides some background material that is relevant to subsequent chapters.

\end{document}