%frontmatter

\documentclass[../main/main.tex]{subfiles}

\begin{document}

\section*{Copyright}
\cleardoublepage

\section*{Disclaimer}
The views discussed in this master thesis are that of the author's.  They do not in anyway represent the views of the United States Air Force Research Laboratory (AFRL) in Rome, NY or  Professor Shiu-Kai Chin from the College of Engineering and Computer Science at Syracuse University.  They are also the sole written work of the author and thus do not represent the views of the other participants in this research.

\cleardoublepage

\section*{Acknowledgements}
This research began in the summer of 2017 as part of the Assured by Design (ABD) program funded by the United States Air Force Research Laboratory (AFRL) in Rome, NY and managed by the principal investigator Professor Shiu-Kai Chin from the College of Engineering and Computer Science at Syracuse University.  This project was envisioned by Professor Shiu-Kai Chin to satisfy the needs of the ABD program.  This master thesis evolved directly from this work.

Thanks and recognition go to the following people for their contribution to this project.\\
Professor Shiu-kai Chin for providing me with the opportunity and for his faith in me and my capabilities on this project.  Erich Devendorf at AFRL for making the ABD program happen. Mizra Tihic for making this happen, especially with respect to funding.

To properly acknowledge the contribution of others requires some description of the workflow.  The actual work began as a collaboration between the subject matter expert from the United States Army and me, the author of this master thesis.  The subject matter expert was Jesse Nathaniel Hall, a Captain [rank?] in the United States Army and also a graduate student in the iSchool (School of Information Science) at Syracuse University. Given the objective of demonstrating CSBD on the patrol base operation (or demonstrating its failure), we collaborated on the \glsentrylong{sse} (SSE) goals of the project.  This work comprised a significant part of this research and is describe in the chapter on Systems Security Engineering.  From thereon, the work was divided among the two of us with weekly updates and collaboration to resolve any potential conflicts.   Jesse modeled the patrol base operations in Visio based on his interpretations of the patrol base operations in the Ranger Handbook \cite{rangermanual}.  A diagram of his work was included as a Visio file with this project.  In addition, a squished version of this diagram was included in the chapter on the Patrol Base Operations.  The result of this work was discussed in this context.   On the other hand, I focused on the actual application of CSBD to the model as it was being developed.  I continued to work on this aspect of the project after collaboration ceased.  

In addition to the work done by Jesse and myself, another student worked with us on the project.  This was YiHong Guo, an undergraduate student in the College of Engineering and Computer Science at Syracuse University. He helped us organize the original documentation of this work in LaTeX, a rather large project. (That documentation is separate from this master thesis.)

\end{document}
